Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-06-15 tex/figures.tex
add noise realizations plot to manuscript

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/sfig_b192-g242_225_cal.png}
\caption{Posterior PDFs obtained from multiple noise realizations of the
  mock photometry and uncalibrated spectra, for a single set of
  parameters.  The input mock parameters are shown as a 
  vertical line, medians of the posterior CDF for each realization are
  shown as dotted lines.
\label{fig:noise_realizations}}
\end{figure*}

>>>>

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/noise_realizations.pdf}
\caption{Percentiles of the posterior PDFs for four of the parameters,
  obtained from multiple noise realizations of the
  mock photometry and uncalibrated spectra.  The input mock parameters are shown as a 
 black horizontal line, The red shaded region gives the 16th to 84th percentile
 range for a noiseless mock.
\label{fig:noise_realizations}}
\end{figure*}

### 2015-06-15 tex/ms.tex
summary plotting for varied physical parameters, start on noisy mocks and change to using the NGC1851 calibration vector for mocks
add noise realizations plot to manuscript

%figures
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\newcommand{\excluster}{NGC7089}

@@

\item Do this for a bunch of ages, metallicities, and dust
  attenuations, possibly compare to the ideal posteriors in each case.

@@

>>>>

%figures
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png,.pdf}
\newcommand{\excluster}{NGC1851}

@@

\item \sout{Do this for a bunch of ages, metallicities, and dust
  attenuations, possibly compare to the ideal posteriors in each case.}

@@

\item \sout{Mock uncalibrated data: do the inference with multiple noise
  realizations to see how the recovered PDFs cover the true value.}
